%-------------------------
% Rover Resume - Star Template
% Link: https://github.com/subidit/rover-resume
%-------------------------

\documentclass[11pt]{article}

\usepackage[sfdefault,semibold,lf]{FiraSans}
\usepackage[a4paper,margin=1in]{geometry}

\usepackage{xcolor}
\definecolor{accent}{HTML}{141E61}

\usepackage{tabularx}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

\newcommand{\linkicon}{
  \color{gray}{\footnotesize\raisebox{1pt}{\faIcon{external-link-alt}}}
}

\setcounter{secnumdepth}{0}
\pdfgentounicode=1

%====== LIST FORMATTING ======
\usepackage{enumitem}
\setlist[itemize]{nosep, left=0pt .. 1.5em}
\setlist[enumerate]{left=0pt..1.5em}
\setlist[description]{itemsep=0pt}

%====== TITLE FORMATTING ======
\usepackage{xhfill}
\usepackage{soul}
\newcommand{\midrule}[1]{
  \leavevmode
  \xrfill[.5ex]{1pt}[accent]~\so{#1}~\xrfill[.5ex]{1pt}[accent]
}

\usepackage{titlesec}
\titlespacing{\section}{0pt}{*4}{*1}
\titlespacing{\subsection}{0pt}{*3}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
\titleformat{\section}{\large\bfseries\uppercase}{}{}{\midrule}
\titleformat*{\subsection}{\large\bfseries\scshape}

%====== CUSTOM COMMANDS ======
\newcommand{\aux}[1]{
  $|$ \space {\normalfont\itshape #1}%
}
\newcommand{\rside}[1]{
  \hfill {\normalfont\color{accent} #1}%
}
\newcommand{\cvsubsection}[3]{%
  \vspace{1em}%
  \noindent
  \begin{tabularx}{\textwidth}{@{}Y r@{}}
    {\normalfont\bfseries #1 \aux{#2}} & {\normalfont\color{accent} #3} \\
  \end{tabularx}%
  \vspace{0.5em}%
}

%====== FOOTER ======
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\small\color{gray} Ian Soares -- Page \thepage\ of \pageref*{LastPage}}

%====== PACKAGES ======
\usepackage{fontawesome5}
\usepackage[bookmarks=false,hidelinks]{hyperref}

%====== DOCUMENT START ======
\begin{document}

%====== BANNER ======
\begin{center}
  {
    \fontsize{36}{12}\fontseries{heavy}\selectfont\color{accent}
    IAN SOARES
  } \\ \medskip

  % substitua pelos seus contatos
  \href{https://wa.me/5531998490641}{{\color{gray}{\faPhone}} +55 (31) 99849-0641} \quad
  \href{mailto:ianptkcs@gmail.com}{{\color{gray}{\faEnvelope}} ianptkcs@gmail.com} \quad
  \href{https://github.com/ianptkcs}{{\color{gray}{\faGithub}} Github/ianptkcs} \quad \\
  \href{https://linkedin.com/in/ianptkcs}{{\color{gray}{\faLinkedin}} LinkedIn/ianptkcs} \quad
  \href{https://portfolio-red-bice-eight.vercel.app/}{{\color{gray}{\faBriefcase}} portfolio}
\end{center}

%====== SECTION: Education ======
\section{Education}

\cvsubsection{Technological Institute of Aeronautics (ITA)}{BSc in Computer Engineering (INCOMPLETE)}{03/2024 -- 12/2024}
\begin{itemize}
  \item Studied basic engineering cycle.
  \item Participated in initiatives like CASD and ITA Bits.
  \item Left to pursue a more computing-focused curriculum.
\end{itemize}


%====== SECTION: Experience ======
\section{Experience}

\cvsubsection{Ensino Ágil}{Fullstack Developer}{01/2025 -- Today}
\begin{itemize}
  \item Spearheaded the modernization of the platform’s UI/UX.
  \item Refactoring legacy pages, thereby enhancing usability and performance.
  \item Designed new modern, rich, interactive interfaces, notably the Checkout and AVE Dashboard.
\end{itemize}


%====== SECTION: Projects ======
\section{Projects}

\cvsubsection{Red Lib}{Personal Project}{06/2025 -- Today}
\begin{itemize}
  \item Developing an integrated library platform to track shows, anime, books and other media in one place.
\end{itemize}


\cvsubsection{Portfolio}{Personal Project}{06/2025 -- Today}
\begin{itemize}
  \item Developed a responsive, modern portfolio website to showcase projects and skills.
  \item Implemented key features using DaisyUI, SolidStart, bunSQLite and Drizzle.
\end{itemize}


\end{document}
